When Subgraph Isomorphism is Really Hard, and Why This Matters for Graph Databases\thanks{Part of this paper appeared at IJCAI \citep{DBLP:conf/ijcai/McCreeshPT16}; \cref{section:introduction} has been expanded and \cref{section:models,section:labelled,section:filterverify} are new material.}

### 2017-07-25 paper/paper.tex
Title

\jairheading{1}{2016}{0-0}{0/0}{0/0}
\ShortHeadings{Why Real-World Subgraph Isomorphism is Easy}
{McCreesh, Prosser \& Trimble}
\firstpageno{1}

@@

\title{Why Real-World Subgraph Isomorphism is Easy, and \\ What This Means for Filter / Verify in
Graph Databases \thanks{Part of this paper appeared at IJCAI
\citep{DBLP:conf/ijcai/McCreeshPT16}; \cref{section:introduction} has been expanded and
\cref{section:models,section:labelled,section:filterverify} are new material.}}

>>>>

\jairheading{1}{2016}{0-0}{0/0}{0/0}
\ShortHeadings{When Subgraph Isomorphism is Really Hard}
{McCreesh, Prosser \& Trimble}
\firstpageno{1}

@@

\title{When Subgraph Isomorphism is Really Hard, and Why This Matters for Graph
Databases\thanks{Part of this paper appeared at IJCAI \citep{DBLP:conf/ijcai/McCreeshPT16};
\cref{section:introduction} has been expanded and
\cref{section:models,section:labelled,section:filterverify} are new material.}}
